Neural Network to Sparse Gaussian Process: For Online Exploration

### 2023-04-16 paper/main.tex
small fix

%List the contributions.
The contributions of the paper our is as follows:
\begin{itemize}
\item We show how to take a trained neural network and convert it to a dual sparse GP. We are able to do this without retraining the GP. Our sparse GP uses the variational formulation, and thus gives better uncertainty estimates than other no variational sparse approaches used previously.
\item Our sparse GP now gives us a compact representation of our parameters in the function space. We can therefore take advantage of the dual parameters formulation for fast conditioning of new data in to our posterior. Crucially this allows for fast adaptation of models that our used in sequential decision making. We show how this is effective in the planning stage of model-based reinforcement exploration.
\end{itemize}

>>>>

%List the contributions.
The contributions of the paper our is as follows:
\begin{itemize}
\item We show how to take a trained neural network and convert it to a dual sparse GP. We are able to do this without retraining a variational objective for the Sparse GP. Our sparse GP uses the variational formulation, and thus gives better uncertainty estimates than other no variational sparse approaches used previously.
\item The sparse GP now gives us a compact representation of our parameters in the function space. We can therefore take advantage of the dual parameters formulation for fast conditioning of new data in to our posterior avoiding retraining of the neural network. Crucially this allows for fast adaptation of models that our used in sequential decision making. We show how this is effective in the planning stage of model-based reinforcement exploration.
\end{itemize}
